Identifying European Sustainable Mega-city Regions with Multi-dimensional Network Percolation

### 2019-03-16 Docs/Papers/Percolation/paper.tex

When considering the aggregated indicators for a parametrization of endogenous city regions, one can relate them to morphological indicators for population density spatial distribution, computed by~\cite{raimbault2018calibration}, that we average on areas. This establishes a link between urban morphology and sustainibility. A principal component analysis on considered points yield 96\% of variance with two components, and 73\% explained by the first component alone. The first component relates to a level of monocentricity ($PC1 = -0.3\cdot I + 0.54 \cdot \bar{d} + 0.51\cdot \varepsilon + 0.59 \cdot \alpha$). As shown in Fig.~\ref{fig:emissions-pc1}, there seems to exist an optimal intermediate level of monocentricity regarding emissions only, except for long-range and low-hierarchy interactions. However, when considering both emissions and economic indicators, urban form then acts as a compromise variable, moving points on Pareto fronts, as shown in Fig.~\ref{fig:paretos-relative}. In some case, highly monocentric areas can be a good compromise, whereas the intermediate optimal for emissions may yield highly inefficient areas.

@@

%Morphological trade-offs

%\textit{No ``optimal'' cities, different forms yield different compromises in terms of relative indicators.}

@@

>>>>

When considering the aggregated indicators for a parametrization of endogenous city regions, one can relate them to morphological indicators for population density spatial distribution, computed by~\cite{raimbault2018calibration}, that we average on areas. This establishes a link between urban morphology and sustainibility. A principal component analysis on considered points yield 96\% of variance with two components, and 73\% explained by the first component alone. The first component relates to a level of monocentricity ($PC1 = -0.3\cdot I + 0.54 \cdot \bar{d} + 0.51\cdot \varepsilon + 0.59 \cdot \alpha$).

@@

As shown in Fig.~\ref{fig:emissions-pc1}, there seems to exist an optimal intermediate level of monocentricity regarding the normalized indicator for emissions only, except for long-range and low-hierarchy interactions.

@@

However, when considering both emissions and economic indicators, urban form then acts as a compromise variable, moving points on Pareto fronts, as shown in Fig.~\ref{fig:paretos-relative}. In some case, highly monocentric areas can be a good compromise, whereas the intermediate optimal for emissions may yield highly inefficient areas. This unveils morphological trad-offs, confirming that there is no optimal urban form, but different compromises regarding the conflicting indicators.
